### 2016-02-29 documentation/EnTrI/EnTrI.tex
Added code to study the insertion position bias and compare clusters with EC numbers

\section{Are EnTrI results biased?}
Since transposon insertion biases can affect the essentiallity level inferred from transposon mutagenesis experiments, the dataset has been tested for two types of biases: the distance from the origin and GC content. The distance bias in every individual strain is depicted in Figure~\ref{fig:distance_bias_individual}. These plots indicate that the bias is negligible in some strains like Salmonella typhi, while the insertion indices of the genes in other strains need to be normalised by their distances from the origin. We have used the LOESS curve and for each strain, divided the insertion indices by the predicted LOESS value to normalise the insertion indices. As the distribution of new insertion indices will be around 1, we have multiplied the resulted values by the mean of the initial insertion indices to have a distribution around the mean. The results are shown in Figure~\ref{fig:normalised_distance_bias}.

@@

>>>>

\section{Are EnTrI results biased?}
Since transposon insertion biases can affect the essentiallity level inferred from transposon mutagenesis experiments, the dataset has been tested for three types of biases: the distance from the origin, GC content, and the position of insertions in genes. The distance bias in every individual strain is depicted in Figure~\ref{fig:distance_bias_individual}. These plots indicate that the bias is negligible in some strains like Salmonella typhi, while the insertion indices of the genes in other strains need to be normalised by their distances from the origin. We have used the LOESS curve and for each strain, divided the insertion indices by the predicted LOESS value to normalise the insertion indices. As the distribution of new insertion indices will be around 1, we have multiplied the resulted values by the mean of the initial insertion indices to have a distribution around the mean. The results are shown in Figure~\ref{fig:normalised_distance_bias}.

@@

The bias towards the position of insertions within genes has been studied since the genes can tolerate lower number of insertions at the start of the gene. We have divided our genes into 3 parts: first 60 nucleotides, last 60 nucleotides, and the rest and plotted the normalised number of insertions in each of these groups. Figure~\ref{fig:insertion-position-bias} summarises the results.

\begin{figure*}
\centering
\begin{tabular}{c c}
\includegraphics[scale=.45, page = 1]{insertion-position-bias.pdf} &
\includegraphics[scale=.45, page = 2]{insertion-position-bias.pdf} \\
\includegraphics[scale=.45, page = 3]{insertion-position-bias.pdf} &
\includegraphics[scale=.45, page = 4]{insertion-position-bias.pdf}
\end{tabular}
\caption{We have divided our genes into 3 parts: first 60 nucleotides (position 1-60), last 60 nucleotides (position 121-180), and the rest (position 61-120) and plotted the normalised number of insertion sites in each of these groups.}
\label{fig:insertion-position-bias}
\end{figure*}
